Allocation Removal by Partial Evaluation in a Tracing JIT

### 2010-10-14 talk/pepm2011/paper.tex
fix XXX, rename section

            $^c$Open End, Göteborg, Sweden
           }
           {cfbolz@gmx.de \and anto.cuni@gmail.com \and fijal@merlinux.eu,
           leuschel@cs.uni-duesseldorf.de \and samuele.pedroni@gmail.com \and arigo@tunes.org}

@@

In Section~\ref{sec:support} we describe some supporting techniques that are not
central to the approach, but are needed to improve the results. The introduced
techniques are evaluated in Section~\ref{sec:Evaluation} using PyPy's Python
interpreter as a case study.

@@

\section{Supporting Techniques}
\label{sec:support}

\subsection{Virtualizables}
\label{sub:Virtualizables}

@@

% subsection Virtualizables (end)

% section Supporting Techniques (end)

@@

In addition to the count of operations we also performed time measurements.
All benchmarks were run 50 times in the same process, to give the JIT time to produce machine
code. The arithmetic mean of the times of the last 30 runs were used as the
result. The errors were computed using a confidence interval with a 95\%
confidence level \cite{georges_statistically_2007}. The results are reported in Figure~\ref{fig:times}.
With the optimization turned on, PyPy's Python interpreter outperforms CPython
in all benchmarks except spambayes (which heavily relies on regular expression
performance and thus is not helped much by our Python JIT) and meteor-contest.
All benchmarks are improved by the allocation removal optimization, some as much
as XXX. XXX Psyco

>>>>

            $^c$Open End, Göteborg, Sweden
           }
           {cfbolz@gmx.de \and anto.cuni@gmail.com \and fijal@merlinux.eu \and
           leuschel@cs.uni-duesseldorf.de \and samuele.pedroni@gmail.com \and arigo@tunes.org}

@@

In Section~\ref{sec:frames} we describe some supporting techniques that are not
central to the approach, but are essential to improve the results. The introduced
techniques are evaluated in Section~\ref{sec:Evaluation} using PyPy's Python
interpreter as a case study.

@@

\section{Taming Frame Objects}
\label{sec:frames}

@@

% section Taming Frame Objects (end)

@@

In addition to the count of operations we also performed time measurements.
All benchmarks were run 50 times in the same process, to give the JIT time to produce machine
code. The arithmetic mean of the times of the last 30 runs were used as the
result. The errors were computed using a confidence interval with a 95\%
confidence level \cite{georges_statistically_2007}. The results are reported in
Figure~\ref{fig:times}. In addition to the run times the table also reports the
speedup that PyPy with optimization turned on achieves.
With the optimization turned on, PyPy's Python interpreter outperforms CPython
in all benchmarks except spambayes (which heavily relies on regular expression
performance and thus is not helped much by our Python JIT) and meteor-contest.
All benchmarks are improved by the allocation removal optimization, by at least
20\% and by as much as a factor of 6.95.

Psyco is able to outperform PyPy's JIT in five out of 14 benchmarks. We hope to
overtake Psyco (which is no longer being actively developped) by adding some
further optimizations.
